Multi-Agent Path Finding with Matching using Increasing Cost Tree Search

### 2021-06-07 docs/paper.tex
Worked on describing experiments and exhaustive variant descr., added plots of results

	In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instance have to be solved. However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound for the SIC of nodes, effectively depth-limiting the ICT traversal.

@@

	\section{Experimental results}
	\section{Responsible Research}
	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project. Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.

>>>>

	In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or marked as unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved. However, once the first solution is found with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound for the SIC of nodes. Formally, let $B = \infty$ represent the initial SIC bound of the ICT search. After solving $C_m$, let $B_{new} = \min(B,C_m)$. By successively contracting this upper-bound on solution SIC, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly.

	 the effort needed to solve the remaining matchings can greatly be reduced.

	 and effectively depth-limiting the ICT traversal.

@@

	\section{Experimental results}
	Because MAPFM lies on the fringe of pathfinding research, no standard benchmarks appear to exist. For MAPF there are the Moving AI benchmarks \cite{sturtevant2012} and potentially a new MAPFM standard benchmark could be defined by generating suitable partitions of agents into teams for these MAPF instances. It was noticed however that optimally solving even small MAPFM instances with comparatively few agents and short distances to goals was computationally already a challenge. This observation informed the creation of a map generator within the peer group

	\begin{figure*}
		\centering
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/open-1}
			\caption{Open, 1 team}
			\label{fig:problem}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/open-3}
		\caption{Open, 3 teams}
		\label{fig:problem}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/obstacle-1}
			\caption{Obstacle, 1 team}
			\label{fig:ict2}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/results/obstacle-3}
		\caption{Obstacle, 3 teams}
		\label{fig:ict2}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-1}
			\caption{Maze, 1 team}
			\label{fig:mdds}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/maze-3}
			\caption{Maze, 3 teams}
			\label{fig:mdds}
		\end{subfigure}

		\caption{Average solving time of algorithm variants on various types of 20x20 grids with a 30s timeout}
		\label{fig:bottom}
	\end{figure*}
	\section{Responsible Research}
	In experiments used to compare the different MAPFM algorithms within the peer group, care was taken to make the comparison fair: all algorithms are implemented in Python 3 and run on the same system: a server with a 12-core Intel Xeon E5-2683 with 8Gb of RAM dedicated to running experiments for this project. Still, some implementations might be more optimized than others so this might be a factor in performance characteristics and in particular in relative performance differences.
